Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-04-29 papers/ms.tex
update ms

The discovery and characterization of planets younger than a billion
years is a major frontier in current exoplanet research.  The reason
is that the properties of young planets provide benchmarks for studies
of planetary evolution.  For instance, young planets can inform our
understanding of when hot Jupiters arrive on their close-in orbits
\citep{dawson_johnson_2018}, how the sizes of planets with massive
gaseous envelopes evolve \citep{rizzuto_tess_2020}, the timescales for
close-in multiplanet systems to fall out of resonance
\citep{arevalo_stability_2022,goldberg_architectures_2022}, and
whether and how mass-loss explains the radius valley
\citep{lopez_how_2012,Owen_Wu_2013,Fulton_et_al_2017,ginzburg_corepowered_2018,lee_primordial_2021}.

@@

Here, we expand on our earlier study of a $38^{+7}_{-6}$ Myr old
Neptune-sized planet in the Kepler field (Kepler-1627~Ab;
\citealt{bouma_kep1627_2022}).  This planet's age was derived based on
its host star's membership in the $\delta$\ Lyr\ cluster.  While our
analysis of the cluster focused on the immediate vicinity of
Kepler-1627 in order to have a reasonable scope,  it became clear that
the $\delta$\ Lyr\ cluster seems to also be part of a much larger
group of similarly aged stars.  This group, which is at a distance of
$\sim$330\,pc from the Sun, spans Cepheus to Hercules (galactic
longitudes, $l$, between 40$^\circ$ and 100$^\circ$), at galactic
latitudes between 0$^\circ$ and 20$^\circ$.  We therefore refer to it
as the Cep-Her complex.  It exhibits significant sub-structure over
its $\approx$250 parsec length, and a detailed analysis of its
memberships, kinematics, and possible origin is currently being
prepared by R.~Kerr and collaborators.

@@

The possibility that the $\delta$~Lyr cluster, RSG-5, and the
sub-populations identified by \citet{Kerr2021} share a common origin
has yet to be fully substantiated, and is the subject of the upcoming
study by R.~Kerr and collaborators.  Our primary interest in the
region stems from the fact that a portion of it was observed by Kepler
(Figure~\ref{fig:XYZvtang}, top panel).  To further explore the
population of stars that were observed, we select candidate Cep-Her
members through four steps, the first three being identical to those
described in Section~3 of \citet{Kerr2021}.  We briefly summarize them
here.

@@

The second step is to perform an unsupervised HDBScan clustering on
the photometrically selected population
\citep{campello_hierarchical_2015,mcinnes_hdbscan_2017}.  The
parameters we use in the clustering are $\{ X, Y, Z, c v_b, c v_{l^*}
\} $, where $c$ is the size-velocity corrective factor, which is taken
as $c=6\,{\rm pc / km\,s}^{-1}$ to ensure that the spatial and
velocity scales have identical standard deviations.  Positions are
computed assuming the \texttt{astropy v4.0} coordinate standard
\citep{astropy_2018}, which places the Sun $8122$ pc from the galactic
center, and assumes the solar velocity with respect to the local
standard of rest from \citet{schonrich_local_2010}.  As input
parameters to HDBScan, we set the minimum $\epsilon$ threshold past
which clusters cannot be fragmented as $25$\,pc in physical space, and
$c$\,\kms\ in velocity.  The minimum cluster size $N$ is set to 10, as
is $k$, the parameter used to define the ``core distance'' density
metric.

This unsupervised clustering in our case yielded 8 distinct groups.
These groups are then used as the ``seed'' populations for the third
step, which is to search for objects at least as close to the 10$^{\rm
th}$ nearest HDBSCAN-identified member in space-velocity coordinates.
This third step yields stars that are spatially and kinematically
close to the photometrically young stars, but which cannot be
identified as young based on their positions in the color--absolute
magnitude diagram.

The outcome of the analysis up to the point of the third step is shown
in Figure~\ref{fig:XYZvtang}.  To enable a selection cut that filters
out field-star contaminants, we also compute a weight metric,
$\alpha$, defined such that the group member with the smallest core
distance has $\alpha=1$, the group member with the greatest core
distance has $\alpha=0$, and weights for the other group members are
log-normally distributed between these two extremes.  After applying a
set of quality cuts on the astrometry and
photometry,\footnote{$\varpi/\sigma_\varpi>5$; $G/\sigma_{G}>50$;
$G_{\rm RP}/\sigma_{G_{RP}}>20$; $G_{\rm BP}/\sigma_{G_{BP}}>20$.}
this procedure yields $\alpha \sim \log_{10}\mathcal{N}(-1.55,0.61)$.
To visualize the results, in Figure~\ref{fig:XYZvtang} we show
12{,}436 objects with $\alpha>0.02$ as gray points, and 
4{,}763 objects with $\alpha>0.10$ as black points.  The previously
known $\delta$~Lyr\ cluster is visible at $(l,b)=(68^\circ,15^\circ$)
and $(v_{l'}, v_b)=(-4.5 ,-4 )\mkms$.  RSG-5 is visible at
$(l,b)=(83^\circ,6^\circ)$, $(v_{l'}, v_b)=(5.5 ,-3.5 )\mkms$.  Most
of the other subclusters, including in Cep-Cyg
($l,b=90^\circ,7^\circ$) and Cerberus ($l,b=48^\circ,18^\circ$) are
too small or dispersed to have previously been analyzed in great
detail.

@@

%
% Numbers are from RSG-5_auto_XYZ_vl_vb_cut.csv,
% CH-2_auto_XYZ_vl_vb_cut.csv
%
We define two sets of stars in the local vicinity of our objects of
interest.  For candidate RSG-5 members, we require:
\begin{align}
  X/{\rm pc} &\in [45, 75] \nonumber \\
  Y/{\rm pc} &\in [320, 350] \nonumber \\
  Z/{\rm pc} &\in [40, 80] \nonumber \\
  v_b/{\rm km\,s^{-1}} &\in [-4, -2.5] \nonumber \\
  v_{l^*}/{\rm km\,s^{-1}} &\in [3.5, 6], \nonumber
\end{align}
though the cluster does have a greater spatial extent toward smaller
$X$ (Figure~\ref{fig:XYZvtang}, middle panels).  For the diffuse stars
near KOI-7368 and KOI-7913, we require
\begin{align}
  X/{\rm pc} &\in [20, 70] \nonumber \\
  Y/{\rm pc} &\in [230, 270] \nonumber \\
  Z/{\rm pc} &\in [75, 105] \nonumber \\
  v_b/{\rm km\,s^{-1}} &\in [-3.5, -1.5] \nonumber \\
  v_{l^*}/{\rm km\,s^{-1}} &\in [2, 6] \nonumber
\end{align}
and we call this latter set of stars ``CH-2''.  These cuts yield
\nrsgfive\ candidate RSG-5 members, and \nchtwo\ candidate CH-2
members.  These stars are listed in Appendix~\ref{app:members}, as are
the Cep-Her candidates that were observed by Kepler.  An important
consideration, especially for CH-2, is the contamination rate by field
stars.  We assess this in the following section.

@@

The lower panels of Figure~\ref{fig:age} show the results.  In RSG-5,
41/47 stars have rotation periods faster than the Pleiades (87\%).
This numerator omits the two stars with periods $>$$12$\,days visible
in the lower-left panel of Figure~\ref{fig:age}.  The age
interpretation for these latter stars, particularly the $\approx$M2.5
dwarf, is not obvious.  \citet{rebull_usco_2018} for instance have
found numerous M-dwarfs with 10-12 day rotation periods at ages of
USco ($\sim$$8$\,Myr), and some may still exist at ages of LCC
($\sim$$16$\,Myr; L.~Rebull in preparation).  Regardless, since
nearly no field star outliers seem to be present on the RSG-5 CAMD,
the fact that we do not detect rotation periods for $\approx$13\% of
stars should perhaps be taken as an indication for the fraction of
stars for which rotation periods might not be detectable, due to
{e.g.}, pole-on stars having lower amplitude starspot modulation.

@@

\paragraph{Spectra}
For Kepler-1643, we acquired two iodine-free spectra from Keck/HIRES
on the nights of 2020 Aug 16 and 2021 Oct 25.  The acquisition and
analysis followed the usual techniques of the California Planet Survey
\citep{howard_cps_2010}.  We derived the stellar parameters ($T_{\rm
eff}, \log g, R_\star$) using \texttt{SpecMatch-Emp}
\citep{yee_SM_2017}, which yielded values in $<$$1$-$\sigma$ agreement
with those from the cluster-isochrone method.  This approach also
yielded $[{\rm Fe/H}]=0.13 \pm 0.09$.  Using the broadened synthetic
templates from \texttt{SpecMatch-Synth} \citep{petigura_cksi_2017}, we
found $v\sin i = 9.3 \pm 1.0\,\mkms$.  The systemic radial velocity at
the two epochs was $-9.1 \pm 1.9\,\mkms$ and $-7.8\pm 1.2\,\mkms$
respectively.  To infer the equivalent width of the \ion{Li}{1}
6708\,\AA\ doublet, we followed the procedure described by
\citet{bouma_2021_ngc2516}.  This yielded a strong detection: ${\rm
EW}_{\rm Li} = 130^{+6}_{-5}$\,m\AA, with values consistent at
$<$$1$-$\sigma$ between the two epochs.   The quoted value does not
correct for the \ion{Fe}{1} blend at 6707.44\,\AA, because HIRES
resolves the two features.  Given the purported age and effective
temperature of the star, the lithium equivalent width is somewhat low.
We discuss this in greater depth in Appendix~\ref{app:spectra}.

@@

		\vspace{-1.27cm}	
		\subfloat{
			\includegraphics[width=0.33\textwidth]{f3c.pdf}
			\includegraphics[width=0.33\textwidth]{f3d.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Raw and processed light curves for the Kepler Objects of
    Interest in Cep-Her.}   
    {\it Top}: 50 day light curve segment from the 3.9 years of Kepler
    data.  The ordinate shows the \texttt{PDCSAP} median-subtracted
    flux in units of parts-per-thousand ($\times 10^{-3}$).  The
    dominant signal is induced by starspots.  {\it Bottom}:
    Phase-folded transits of Kepler-1643, KOI-7913, KOI-7368, and
    Kepler-1627 with stellar variability removed.  The maximum {\it a
    posteriori} transit model is shown with the gray line, and the
    residual after subtracting the transit model is vertially
    displaced.  Windows over 10 hours are shown.  Gray points are
    individual flux measurements; black points are binned to 20 minute
    intervals, and have a representative 1-$\sigma$ error bar in the
    center-right of each panel. 
		\label{fig:planets}
	}
\end{figure*}

@@

We fitted the data using \texttt{exoplanet}
\citep{exoplanet:exoplanet}.  We assumed a Gaussian likelihood, and
sampled using \texttt{PyMC3}'s No-U-Turn Sampler
\citep{hoffman_no-u-turn_2014}, after having initialized to the the
maximum {\it a posteriori} (MAP) model.  We used the
\citet{gelman_inference_1992} statistic, $\hat{R}$, as our convergence
diagnostic.  The resulting fits are shown in the lower panels of
Figure~\ref{fig:planets}, and the important derived parameters are in
Table~\ref{tab:sysparams}.  The set of full parameters and their
priors are given in Appendix~\ref{app:transit}.

@@

\subsection{Is CH-2 a real cluster?}
\label{subsec:ch2}

@@

Given its low density, in CH-2 really a star cluster?  For this
discussion, we adopt the definition that a star cluster is a group of
at least 12 stars that was physically associated at its time of
formation.  The ``12'' is set to distinguish star clusters from
high-order multiples \citep[see][]{krumholz_star_2019}.  Dissolved
clusters and their tidal tails are therefore included in our concept
of clusters.  We do not however require a threshold number of stars
per unit spatial volume for a group to be a ``cluster''.  The latter
point acknowledges that an important factor in cluster identification
is also the density in velocity space.  Perhaps once stellar rotation
periods and chemical abundances reach the same level of ubiquity as
stellar proper motions, they might enable further refinement of our
ability to discover stars that formed together.

From a data-driven perspective, demonstrating that a group of stars
was physically associated at its time of formation is challenging.
While some young groups show kinematic evidence for expansion
\citep{kuhn_kinematics_2019}, many, including Sco-Cen, do not
\citep{wright_kinematics_2018}.  This complicates the feasibility of
deriving kinematic ages through traceback, as well as through the
expansion itself \citep[see][]{crundall_chronostar_2019}.  A more
minimal approach is that suggested by \citet{tofflemire_2021}: search
for coeval, phase-space neighbors, measure their ages, and determine
if they share a common age.  This approach can demonstrate whether a
star is currently associated with a set of coeval stars, which
is much easier than determining what the association looked like in
the past.  Our analysis of CH-2 meets the latter standard for the
existence of a $\approx$40\,Myr assocation.  It would be a worthy
exercise for future work to perform a similar search for coeval
phase-space neighbors on the entire dataset of known exoplanet hosts.
For the time being, we can offer the anecdotal point that in our
experience, most stars do not have dozens of 40\,Myr neighbors within
a local volume of a few \kms\ and tens of parsecs.

@@

%\clearpage
\acknowledgements
\raggedbottom
% Cycle 3 and 4
L.G.B{.} acknowledges support from the Heising-Simons Foundation 51 Pegasi~b
Fellowship
and the TESS GI Program (NASA grants
80NSSC21K0335 and 80NSSC22K0298).
J.L.C{.} is supported by NSF AST-2009840 and NASA TESS G04217. 
%
% ACKNOWLEDGE PFS / CAMPANAS.
%
This paper also includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
We thank the TESS Architects
%(G.~Ricker, R.~Vanderspek, D.~Latham, S.~Seager, J.~Jenkins)
and the many TESS team members for their
efforts to make the mission a continued success.
%
%
%This study was based in part on observations at Cerro Tololo
%Inter-American Observatory at NSF's NOIRLab (NOIRLab Prop{.} ID
%2020A-0146; 2020B-0029 PI: Bouma), which is managed by the
%Association of Universities for Research in Astronomy (AURA) under a
%cooperative agreement with the National Science Foundation.
%
%
%Finally, this research has made use of the Keck Observatory Archive (KOA),
%which is operated by the W. M. Keck Observatory and the NASA Exoplanet
%Science Institute (NExScI), under contract with the National
%Aeronautics and Space Administration.
Finally, we also thank the Keck Observatory staff for their support of
HIRES and remote observing.  We recognize the importance that the
summit of Maunakea has within the indigenous Hawaiian community, and
are deeply grateful to have the opportunity to conduct observations
from this mountain.
%
% The Digitized Sky Survey was produced at the Space Telescope Science
% Institute under U.S. Government grant NAG W-2166.
% Figure~\ref{fig:scene} is based on photographic data obtained using
% the Oschin Schmidt Telescope on Palomar Mountain.
%

@@

% \input{starparams.tex}
% \input{model_posterior_table.tex}
% \input{t1_appendix.tex}
% \input{t2_appendix.tex}

@@

\paragraph{Table~2} contains candidate Cep-Her members with weights
$\alpha>0.02$ observed by Kepler.  More restrictive weight cuts would
be needed if one wanted to remove the majority of field star
interlopers; at least half of the stars included in the table are
unlikely to be bonafide Cep-Her members.  Table~2  was created by
cross-matching candidate Cep-Her members (selected using Gaia EDR3;
Section~\ref{subsec:members}) against a Kepler to Gaia DR2 cross-match
(the \texttt{gaia-kepler.fun} crossmatch database created by Megan
Bedell).  The \texttt{kic\_dr2\_ang\_dist} column is from the latter
table.  The EDR3 to DR2 match was performed using the
\texttt{gaiaedr3.dr2\_neighbourhood} table, and the closest proper
motion and epoch-corrected angular distance neighbor was taken as the
single best match.  The \texttt{edr3\_dr2\_mag\_diff} column gives
some indication of the reliability of this EDR3 to DR2 conversion, as
there are a few cases between Gaia DR2 and EDR3 where partially
resolved binaries became fully resolved.

\paragraph{Table~3} contains spatial, kinematic, astrometric, and
rotation period information for the \nrsgfive\ candidate RSG-5 members
and \nchtwo\ candidate CH-2 members described in
Section~\ref{subsec:members}.  These are the data used to make the
lower panels of Figure~\ref{fig:age}. 
% Table~3 includes rotation periods for 53 stars with ZTF and 51 stars
% with TESS, for a total of 71 periods reported for unique stars and 32
% overlapping between the surveys.
We adopted the ZTF period over the
TESS period in three cases: (1) Gaia EDR3 2081755809272821248: the
Lomb-Scargle periodogram favored 6.67 days, consistent with the ZTF
period of 6.61 days; however, we flagged it as a candidate
double-dipper, which appears to have inaccurately doubled the TESS
period to 13.34 days; (2) Gaia EDR3 2081737529891330560: we found 3.06
days with TESS and 6.64 days with ZTF; we suspect that TESS captured
the 1/2-period harmonic and adopt the approximately double value from
ZTF; (3) 2134851775526125696: for this star, we measured 1.91 days
with TESS from Cycle 2, but noted that the signal appeared to be
missing in Cycle 4; ZTF found a strong signal at 12.23 days and we
adopt this as the star's period. In the remaining overlap cases, we
adopted the average between TESS and ZTF as the final period. For
these overlap stars, the median absolute deviation is 0.01 days,
showing remarkable consistency between the surveys. For three stars,
we failed to detect a period in TESS but recovered one from ZTF; in
all cases the periods appear to be 13--16 days.  These stars were: (1)
Gaia EDR3 2129930258400157440, for which TESS showed a flat light
curve while ZTF yielded a 15.3-day period; (2) Gaia EDR3
2082376861542398336, LS found a 7.6-day period which we rejected
during visual validation; we found 15.4 days with ZTF, and we suspect
that the weak/rejected signal form TESS might have been a 1/2 period
harmonic; (3) Gaia EDR3 2082397099429013120, similar to the previous
case, we rejected a 6.7-day signal from TESS and recovered a 12.8-day
period with ZTF.

>>>>

The discovery and characterization of planets younger than a billion
years is a major frontier in current exoplanet research.  The reason
is that the properties of young planets provide benchmarks for studies
of planetary evolution.  For instance, young planets can inform our
understanding of when hot Jupiters arrive on their close-in orbits
\citep{dawson_johnson_2018}, how the sizes of planets with massive
gaseous envelopes evolve \citep{rizzuto_tess_2020}, the timescales for
close-in multiplanet systems to fall out of resonance
\citep{izidoro_breaking_2017,arevalo_stability_2022,goldberg_architectures_2022}, and
whether and how mass-loss explains the radius valley
\citep{lopez_how_2012,Owen_Wu_2013,Fulton_et_al_2017,ginzburg_corepowered_2018,lee_primordial_2021}.

@@

Here, we expand on our earlier study of a $38^{+7}_{-6}$ Myr old
Neptune-sized planet in the Kepler field (Kepler-1627~Ab;
\citealt{bouma_kep1627_2022}).  This planet's age was derived based on
its host star's membership in the $\delta$\ Lyr\ cluster.  While our
analysis of the cluster focused on the immediate vicinity of
Kepler-1627 in order to have a reasonable scope,  it became clear that
the $\delta$\ Lyr\ cluster seems to also be part of a much larger
group of similarly aged stars.  This group, which is at a distance of
$\sim$330\,pc from the Sun, spans Cepheus to Hercules (galactic
longitudes, $l$, between 40$^\circ$ and 100$^\circ$), at galactic
latitudes between 0$^\circ$ and 20$^\circ$.  We therefore refer to it
as the Cep-Her complex.  It exhibits significant sub-structure over
its $\approx$250 parsec length, and a detailed analysis of its
memberships, kinematics, and possible origin is currently being
prepared as part of the 1\,kpc expansion of the SPYGLASS project
(R.~Kerr et al.\ in prep).

@@

The possibility that the $\delta$~Lyr cluster, RSG-5, and the
sub-populations identified by \citet{Kerr2021} share a common origin
has yet to be fully substantiated, but preliminary clustering results
from the 1\,kpc SPYGLASS analysis (R.~Kerr et al.\ in prep) suggest
the presence of contiguous stellar populations connecting each of
these groups.  In this work, our primary interest in the region stems
from the fact that a portion of it was observed by Kepler
(Figure~\ref{fig:XYZvtang}, top panel).  To further explore this
sub-population, we select candidate Cep-Her members through four
steps, the first three being identical to those described in Section~3
of \citet{Kerr2021}.  We briefly summarize them here.

@@

The second step is to perform an unsupervised HDBScan clustering on
the photometrically selected population
\citep{campello_hierarchical_2015,mcinnes_hdbscan_2017}.  The
parameters we use in the clustering are $\{ X, Y, Z, c v_b, c v_{l^*}
\} $, where $c$ is the size-velocity corrective factor, which is taken
as $c=6\,{\rm pc / km\,s}^{-1}$ to ensure that the spatial and
velocity scales have identical standard deviations.  Positions are
computed assuming the \texttt{astropy v4.0} coordinate standard
\citep{astropy_2018}, which places the Sun $8122$ pc from the galactic
center, and assumes the solar velocity with respect to the local
standard of rest from \citet{schonrich_local_2010}.  As input
parameters to HDBScan, we set the minimum $\epsilon$ threshold past
which clusters cannot be fragmented as $25$\,pc in physical space, and
$25/c$\,\kms\ in velocity.  The minimum cluster size $N$ is set to 10, as
is $k$, the parameter used to define the ``core distance'' density
metric.

This unsupervised clustering in this case yielded 8 distinct subgroups.
These groups are then used as the ``seed'' populations for the third
step, which is to search for objects at least as close to the 10$^{\rm
th}$ nearest HDBSCAN-identified member in space-velocity coordinates.
This third step yields stars that are spatially and kinematically
close to the photometrically young stars, but which cannot be
identified as young based on their positions in the color--absolute
magnitude diagram.

The outcome of the analysis up to the point of the third step is shown
in Figure~\ref{fig:XYZvtang}.  To enable a selection cut that filters
out field-star contaminants, we also compute a weight metric,
$D$, defined such that the group member with the smallest core
distance has $D=1$, the group member with the greatest core
distance has $D=0$, and weights for the other group members are
log-normally distributed between these two extremes.  After applying a
set of quality cuts on the astrometry and
photometry,\footnote{$\varpi/\sigma_\varpi>5$; $G/\sigma_{G}>50$;
$G_{\rm RP}/\sigma_{G_{RP}}>20$; $G_{\rm BP}/\sigma_{G_{BP}}>20$.}
this procedure yields $D \sim \log_{10}\mathcal{N}(-1.55,0.61)$.
To visualize the results, in Figure~\ref{fig:XYZvtang} we show
12{,}436 objects with $D>0.02$ as gray points, and 
4{,}763 objects with $D>0.10$ as black points.  The previously
known $\delta$~Lyr\ cluster is visible at $(l,b)=(68^\circ,15^\circ$)
and $(v_{l'}, v_b)=(-4.5 ,-4 )\mkms$.  RSG-5 is visible at
$(l,b)=(83^\circ,6^\circ)$, $(v_{l'}, v_b)=(5.5 ,-3.5 )\mkms$.  Most
of the other subclusters, including in Cep-Cyg
($l,b=90^\circ,7^\circ$) and Cerberus ($l,b=48^\circ,18^\circ$) are
too small or dispersed to have previously been analyzed in great
detail.

@@

%
% Numbers are from RSG-5_auto_XYZ_vl_vb_cut.csv,
% CH-2_auto_XYZ_vl_vb_cut.csv
%
We define two sets of stars in the local vicinity of our objects of
interest.  For candidate RSG-5 members, we require:
\begin{align}
  X/{\rm pc} &\in [45, 75] \nonumber \\
  Y/{\rm pc} &\in [320, 350] \nonumber \\
  Z/{\rm pc} &\in [40, 80] \nonumber \\
  v_b/{\rm km\,s^{-1}} &\in [-4, -2.5] \nonumber \\
  v_{l^*}/{\rm km\,s^{-1}} &\in [3.5, 6], \nonumber
\end{align}
though the cluster does have a greater spatial extent toward smaller
$X$ (Figure~\ref{fig:XYZvtang}, middle panels).  For the diffuse stars
near KOI-7368 and KOI-7913, we require
\begin{align}
  X/{\rm pc} &\in [20, 70] \nonumber \\
  Y/{\rm pc} &\in [230, 270] \nonumber \\
  Z/{\rm pc} &\in [75, 105] \nonumber \\
  v_b/{\rm km\,s^{-1}} &\in [-3.5, -1.5] \nonumber \\
  v_{l^*}/{\rm km\,s^{-1}} &\in [2, 6] \nonumber
\end{align}
and we call this latter set of stars ``CH-2'', using the preliminary 
Cep-Her (CH) subgroup identifier from R.~Kerr et al.\ (in prep).
These cuts yield
\nrsgfive\ candidate RSG-5 members, and \nchtwo\ candidate CH-2
members.  These stars are listed in Appendix~\ref{app:members}, as are
the Cep-Her candidates that were observed by Kepler.  An important
consideration, especially for CH-2, is the contamination rate by field
stars.  We assess this in the following section.

@@

The lower panels of Figure~\ref{fig:age} show the results.  In RSG-5,
41/47 stars have rotation periods faster than the Pleiades (87\%).
This numerator omits the two stars with periods $>$$12$\,days visible
in the lower-left panel of Figure~\ref{fig:age}.  The age
interpretation for these latter stars, particularly the $\approx$M2.5
dwarf, is not obvious.  \citet{rebull_usco_2018} for instance have
found numerous M-dwarfs with 10-12 day rotation periods at ages of
USco ($\sim$$8$\,Myr), and some may still exist at ages of LCC
($\sim$$16$\,Myr; L.~Rebull submitted).  Regardless, since
nearly no field star outliers seem to be present on the RSG-5 CAMD,
the fact that we do not detect rotation periods for $\approx$13\% of
stars should perhaps be taken as an indication for the fraction of
stars for which rotation periods might not be detectable, due to
{e.g.}, pole-on stars having lower amplitude starspot modulation.

@@

\paragraph{Spectra}
For Kepler-1643, we acquired two iodine-free spectra from Keck/HIRES
on the nights of 2020 Aug 16 and 2021 Oct 25.  The acquisition and
analysis followed the usual techniques of the California Planet Survey
\citep{howard_cps_2010}.  We derived the stellar parameters ($T_{\rm
eff}, \log g, R_\star$) using \texttt{SpecMatch-Emp}
\citep{yee_SM_2017}, which yielded values in $<$$1$-$\sigma$ agreement
with those from the cluster-isochrone method.  This approach also
yielded $[{\rm Fe/H}]=0.13 \pm 0.09$.  Using the broadened synthetic
templates from \texttt{SpecMatch-Synth} \citep{petigura_cksi_2017}, we
found $v\sin i = 9.3 \pm 1.0\,\mkms$.  The systemic radial velocity at
the two epochs was $-9.1 \pm 1.9\,\mkms$ and $-7.8\pm 1.2\,\mkms$
respectively \citep{chubak_2012}.  To infer the equivalent width of
the \ion{Li}{1} 6708\,\AA\ doublet, we followed the procedure
described by \citet{bouma_2021_ngc2516}.  This yielded a strong
detection: ${\rm EW}_{\rm Li} = 130^{+6}_{-5}$\,m\AA, with values
consistent at $<$$1$-$\sigma$ between the two epochs.   The quoted
value does not correct for the \ion{Fe}{1} blend at 6707.44\,\AA,
because HIRES resolves the two features.  Given the purported age and
effective temperature of the star, the lithium equivalent width is
somewhat low.  We discuss this in greater depth in
Appendix~\ref{app:spectra}.

@@

		\vspace{-1.27cm}	
		\subfloat{
			\includegraphics[width=0.33\textwidth]{f3c.pdf}
			\includegraphics[width=0.33\textwidth]{f3d.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Raw and processed light curves for the Kepler Objects of
    Interest in Cep-Her.}   
    {\it Top}: 50 day light curve segment from the 3.9 years of Kepler
    data.  The ordinate shows the \texttt{PDCSAP} median-subtracted
    flux in units of parts-per-thousand ($\times 10^{-3}$).  The
    dominant signal is induced by starspots.  {\it Bottom}:
    Phase-folded transits of Kepler-1643, KOI-7913, KOI-7368, and
    Kepler-1627 with stellar variability removed.  The maximum a
    posteriori transit model is shown with the gray line, and the
    residual after subtracting the transit model is vertially
    displaced.  Windows over 10 hours are shown.  Gray points are
    individual flux measurements; black points are binned to 20 minute
    intervals, and have a representative 1-$\sigma$ error bar in the
    center-right of each panel. 
		\label{fig:planets}
	}
\end{figure*}

@@

We fitted the data using \texttt{exoplanet}
\citep{exoplanet:exoplanet}.  We assumed a Gaussian likelihood, and
sampled using \texttt{PyMC3}'s No-U-Turn Sampler
\citep{hoffman_no-u-turn_2014}, after having initialized to the the
maximum a posteriori (MAP) model.  We used the
\citet{gelman_inference_1992} statistic, $\hat{R}$, as our convergence
diagnostic.  The resulting fits are shown in the lower panels of
Figure~\ref{fig:planets}, and the important derived parameters are in
Table~\ref{tab:sysparams}.  The set of full parameters and their
priors are given in Appendix~\ref{app:transit}.

@@

\subsection{Is CH-2 real?}
\label{subsec:ch2}

@@

Given its low density, in CH-2 really a star cluster?  For this
discussion, we adopt the definition that a star cluster is a group of
at least 12 stars that was physically associated at its time of
formation.  The ``12'' is set to distinguish star clusters from
high-order multiples \citep[see][]{krumholz_star_2019}.  We explicitly
do not require a ``star cluster'' to be gravitationally bound:
dissolved clusters as well as their tidal tails are included in our
adopted definition of ``clusters''.  We similarly do not require a
threshold number of stars per unit spatial volume.  The latter point
acknowledges that an important factor in cluster identification is
also density in velocity space.  Perhaps once stellar rotation
periods and chemical abundances reach the same level of ubiquity as
stellar proper motions, they might enable further refinement of our
ability to discover stars that formed as part of the same event.

From a data-driven perspective, demonstrating that a group of stars
was physically associated at its time of formation is challenging.
While some young groups show kinematic evidence for expansion
\citep{kuhn_kinematics_2019}, many, including Sco-Cen, do not
\citep{wright_kinematics_2018}.  This complicates the feasibility of
deriving kinematic ages through traceback, as well as through the
expansion itself \citep[see][]{crundall_chronostar_2019}.  A more
minimal approach is that suggested by \citet{tofflemire_2021}: search
for coeval, phase-space neighbors, measure their ages, and determine
if they share a common age.  This approach can demonstrate whether a
star is currently associated with a set of coeval stars, though it
falls short of determining what the association looked like in
the past.  Our analysis of CH-2 meets the latter standard for the
existence of a $\approx$40\,Myr stellar assocation.  It would be a
worthy exercise for future work to perform a similar search for coeval
phase-space neighbors on the entire dataset of known exoplanet hosts.
For the time being, we can offer the anecdotal point that in our
experience, most stars do not have dozens of 40\,Myr neighbors within
a local volume of a few \kms\ and tens of parsecs.

@@

%\clearpage
\acknowledgements
\raggedbottom
% Cycle 3 and 4
L.G.B{.} acknowledges support from the Heising-Simons Foundation 51
Pegasi~b Fellowship and the TESS GI Program (NASA grants 80NSSC21K0335
and 80NSSC22K0298).
J.L.C{.} is supported by NSF AST-2009840 and the TESS GI Program (NASA
grant 80NSSC22K0299).
%
% ACKNOWLEDGE PFS / CAMPANAS.
%
%This paper includes data collected by the TESS mission, which are
%publicly available from the Mikulski Archive for Space Telescopes
%(MAST).
%%
%Funding for the TESS mission is provided by NASA's Science Mission
%directorate.
%%
%We thank the TESS architects
%%(G.~Ricker, R.~Vanderspek, D.~Latham, S.~Seager, J.~Jenkins)
%and the many TESS team members for their
%efforts to make the mission a continued success.
%
%
%This study was based in part on observations at Cerro Tololo
%Inter-American Observatory at NSF's NOIRLab (NOIRLab Prop{.} ID
%2020A-0146; 2020B-0029 PI: Bouma), which is managed by the
%Association of Universities for Research in Astronomy (AURA) under a
%cooperative agreement with the National Science Foundation.
%
%
%Finally, this research has made use of the Keck Observatory Archive (KOA),
%which is operated by the W. M. Keck Observatory and the NASA Exoplanet
%Science Institute (NExScI), under contract with the National
%Aeronautics and Space Administration.
%We also thank the Keck Observatory staff for their support of
%HIRES and remote observing.  We recognize the importance that the
%summit of Maunakea has within the indigenous Hawaiian community, and
%are deeply grateful to have the opportunity to conduct observations
%from this mountain.
%
% The Digitized Sky Survey was produced at the Space Telescope Science
% Institute under U.S. Government grant NAG W-2166.
% Figure~\ref{fig:scene} is based on photographic data obtained using
% the Oschin Schmidt Telescope on Palomar Mountain.
%

@@

@@

\paragraph{Table~2} contains candidate Cep-Her members with weights
$D>0.02$ observed by Kepler.  The final catalog of candidate
Cep-Her members will be provided by R.~Kerr et al.\ in prep.; Table~2 is
from a preliminary version of that same catalog.  Note that more
restrictive weight cuts should be imposed should one wish to remove
the majority of field star interlopers; at least half of the stars
included in the table are unlikely to be bonafide Cep-Her members.
Table~2  was created by cross-matching candidate Cep-Her members
(selected using Gaia EDR3; Section~\ref{subsec:members}) against a
Kepler to Gaia DR2 cross-match (the \texttt{gaia-kepler.fun}
crossmatch database created by Megan Bedell).  The
\texttt{kic\_dr2\_ang\_dist} column is from the latter table.  The
EDR3 to DR2 match was performed using the
\texttt{gaiaedr3.dr2\_neighbourhood} table, and the closest proper
motion and epoch-corrected angular distance neighbor was taken as the
single best match.  The \texttt{edr3\_dr2\_mag\_diff} column gives
some indication of the reliability of this EDR3 to DR2 conversion, as
there are a few cases between Gaia DR2 and EDR3 where partially
resolved binaries became fully resolved.
